Stuff that may well go into the project report

### 2014-10-24 stuff_somewhat_organised.tex
Får vel organisere stuffet litt bedre.

	\item[Using a compactness argument:] We can conclude that $\{w_n\}_{n \in \mathbb{N}}$ is a bounded sequence in $H^1(Q_T)$, so by theorem \ref{thm:Rellich} it has convergent subsequence $\{w_{n_j}\}_{j \in \mathbb{N}}$ that converges to some $w$ in $L^2(Q_T)$.

@@

	\item[Showing that $w=\Phi(u)$:]

\end{description}

>>>>

	\item[Using a compactness argument:] We can conclude that $\{w_n\}_{n \in \mathbb{N}}$ is a bounded sequence in $H^1(Q_T)$, so by theorem \ref{thm:Rellich} it has convergent subsequence $\{w_{n_j}\}_{j \in \mathbb{N}}$ that converges to some $w$ in $L^2(Q_T)$. The energy estimate continues to hold in the limit as
	\begin{equation}
	\iint_{Q_T}|\nabla w|^2 dxdt \leq \int_\Omega \Psi(u_0)dx + \iint_{Q_T}fw dxdt
	\end{equation}

@@

	\item[Showing that $w=\Phi(u)$:] By the triangle inequality we split $|\Phi(u)-w|$ into
	\begin{equation*}
	|\Phi(u) - w| \leq |\Phi(u) - \Phi(u_{n_j})| + |\Phi(u_{n_j}) - \Phi_{n_j}(u_{n_j})| + |w_{n_j}-w|. 
	\end{equation*}
	Then, integration over $Q_T$ gives
	\begin{align*}
	\iint_{Q_T}|\Phi(u)-w|dxdt &\leq \iint_{Q_T}|\Phi(u)-\Phi(u_{n_j})|dxdt \\
	&+ \iint_{Q_T}|\Phi(u_{n_j})-\Phi_{n_j}(u_{n_j})|dxdt \\
	&+ \iint_{Q_T}|w_{n_j} - w|dxdt.
	\end{align*}
	The first term can be made arbitrarily small by the $L^1$-convergence of $\{u_n\}$ together with $\Phi$ being locally Lipschitz. The last term is controlled by the $L^2$-convergence of $\{w_{n_j}\}$ and that $Q_T$ is bounded. So we need to consider the middle term. We start off with
	\begin{align*}
	|\Phi(u_{n_j}) - \Phi_{n_j}(u_{n_j})| &= \left| \Phi(u_{n_j}) - \int_{\mathbb{R}}\left\{ \Phi(u_{n_j}-y) + \frac{u_{n_j}-y}{n_j} \right\} \eta_{n_j}(y)dy  \right| \\
	&= \left|\int_\mathbb{R}\left\{\Phi(u_{n_j})-\Phi(u_{n_j}-y)-\frac{u_{n_j}-y}{n_j} \right\} \eta_{n_j}(y)dy \right| \\
	&\leq \int_\mathbb{R}\left\{ |\Phi(u_{n_j})-\Phi(u_{n_j}-y)|+\frac{|u_{n_j}-y|}{n_j}\right\} \eta_{n_j}(y)dy.
	\end{align*}
	Since $\Phi$ is locally Lipschitz we get that for any $\epsilon >0$
	\begin{align*}
	|\Phi(u_{n_j}) - \Phi_{n_j}(u_{n_j})| &\leq \int_\mathbb{R}\left\{ L_{\Phi}|y|+\frac{|u_{n_j}-y|}{n_j}\right\} \eta_{n_j}(y)dy \\
	&< L_{\Phi}\epsilon + \frac{|u_{n_j}|}{n_j}+\epsilon
	\end{align*}
	for sufficiently large $n_j$. Here $L_\Phi$ is a Lipschitz constant for $\Phi$. Thus, we can make the bounds on all three terms arbitrarily small, and we are forced to conclude that 
	\begin{equation}
	\iint_{Q_T}|\Phi(u)-w|dxdt = 0,
	\end{equation}	 
	which means that $\Phi(u) = w$ a.e.

	\item[$u$ is a weak solution:] We already know that $u \in L^1(Q_T)$, and $\Phi(u)=w \in L^1(0,T: W^{1,1}(\Omega))$\footnote{Actually, this may not be as easy to see as I've stated here. Need to use yet another estimate to show this.}. So what's left is to show that
	\begin{equation*}
	\iint_{Q_T}\left\{ \nabla\Phi(u) \cdot \nabla \eta - u\partial_t \eta - f\eta \right\}dxdt - \int_\Omega u_0\eta\big|_{t=0}dx = 0
	\end{equation*}
	for any $\eta \in C^1(\overline{Q}_T)$ that vanish on $\partial \Omega \times [0,T)$ and for $t=T$.
\end{description}
